Learning constraints in spreadsheets and tabular data

### 2016-09-16 Paper/ECAI/tabular.tex
Minor fixes

\author{Samuel Kolb \and Sergey Paramonov \and Thias Guns \and Luc De Raedt} % \institute{KULeuven}

@@

We focus on \textit{functional} constraints that could be used as formulas in spreadsheets, ignoring the structural constraints \textit{ALLDIFFERENT}, \textit{FOREIGNKEY} and \textit{PERMUTATION}.
Moreover, we included detected equalities as intended constraints (in 5~spreadsheets).
All experiments were run using Python 3.5.1 on a Macbook Pro, Intel Core i7 2.3~GHz with 16GB RAM.
\sergey{Samuel! Add a reference to python-constraint, including the references list at the end}\\

>>>>

\author{Samuel Kolb \and Sergey Paramonov \and Tias Guns \and Luc De Raedt}
\institute{KULeuven}

@@

We focus on \textit{functional} constraints that could be used as formulas in spreadsheets, ignoring the structural constraints \textit{ALLDIFFERENT}, \textit{FOREIGNKEY} and \textit{PERMUTATION}.
Moreover, we included detected equalities as intended constraints (in 5~spreadsheets).
All experiments were run using Python 3.5.1 on a Macbook Pro, Intel Core i7 2.3~GHz with 16GB RAM.
The constraint solver that is used by the superblock assignment phase is python-constraint\cite{python_constraint}.
